---
title: "Quiz 22"
subtitle: "STAT 201"
author: "Muzi Dang"

format:
  html:
    toc: true
    embed-resources: true

execute:
  message: false
  warning: false
---
Download the file capital_cities.csv from here. Make sure the file is in your current working directory. Execute the following code to obtain the objects coordinates_capital_cities and country_names.

The object country_names is an atomic vector consisting of country names. The object coordinates_capital_cities is a matrix consisting of the latitude-longitude pair of the capital city of the respective country. The order of countries in country_names is the same as the order in which their capital city coordinates (latitude-longitude) appear in the matrix coordinates_capital_cities.

13.6.2.1 Top 10 countries closest to DC
Print the names of the countries of the top 10 capital cities closest to the US capital - Washington DC.

Create and print a matrix containing the coordinates of the top 10 capital cities closest to Washington DC.

Note that:

The Country Name for US is given as United States in the data.
The ‘closeness’ of capital cities from the US capital is based on the Euclidean distance of their coordinates to those of the US capital.
The dataset includes two records: United States and US Minor Outlying Islands, both belonging to the U.S., with a distance of zero. These records must be excluded to accurately identify the closest foreign capital cities.
Hint:

Get the coordinates of Washington DC from coordinates_capital_cities. The row that contains the coordinates of DC will have the same index as United States has in the vector country_names

Create a matrix that has coordinates of Washington DC in each row, and has the same number of rows as the matrix coordinates_capital_cities.

Subtract coordinates_capital_cities from the matrix created in (2). Element-wise subtraction will occur between the matrices.

Use the apply() function on the matrix obtained above to find the Euclidean distance of Washington DC from the rest of the capital cities.

Using the distances obtained above, find the country that has the closest capital to DC (Euclidean distance > 0).

Top 10 countries with capitals closest to Washington DC are the following:

You can also use the following code to exclude the U.S. records

The coordinates of the top 10 capital cities closest to Washington DC are:



Matrix Approach:
```{r}
data <- read.csv("capital_cities(in).csv")
country_names <- data$Country.Name
coordinates_capital_cities <- cbind(data$Capital.Latitude, data$Capital.Longitude)

us_index <- c(which(country_names == "United States"), which(country_names == "US Minor Outlying Islands"))

us_cord <- coordinates_capital_cities[which(country_names == "United States"), ]

country_names <- country_names[-us_index]
coordinates_capital_cities <- coordinates_capital_cities[-us_index, ]

dc_mat <- matrix(us_cord, nrow = nrow(coordinates_capital_cities), ncol = 2, byrow = TRUE)
distance_mat <- coordinates_capital_cities - dc_mat
distances <- apply(distance_mat, 1, function(x) sqrt(sum(x^2)))

print(country_names[order(distances)[1:10]])

```

Data Frame Approach:
```{r}
df <- data.frame(
  Name = data$Country.Name,
  Lat = data$Capital.Latitude,
  Long = data$Capital.Longitude
)

us_index <- c((which(df$Name =="United States")), (which(df$Name == "US Minor Outlying Islands")))
df <- df[-us_index, ]

us_lat <- data$Capital.Latitude[which(data$Country.Name == "United States")]
us_long <- data$Capital.Longitude[which(data$Country.Name == "United States")]

df$Distance <- sqrt((df$Lat - us_lat)^2 + (df$Long - us_long)^2)

print(df$Name[order(df$Distance)[1:10]])

```